Towards a Reinforcement Learning approach for Aggregate Computing

### 2021-11-29 paper-2021-woa-ac-ml.tex
minor: 'an hybrid' => 'a hybrid'

To the best of our knowledge, this is the first effort towards an ``hybrid'' collective programming approach, where the high-level program specification is 
 done by a designer and the low-level matters are left to machine learning algorithms.
%
As such, this work shed light on several issues deserving future investigation.

>>>>

To the best of our knowledge, this is the first effort towards a ``hybrid'' collective programming approach, where the high-level program specification is 
 done by a designer and the low-level matters are left to machine learning algorithms.
%
As such, this work shed light on several issues deserving future investigation.
